A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-30 writeup/paper.tex
Removed old paragraphs

\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries. Turkers' performance on our control tasks is well correlated with this measure of quality. Results are show below in table \ref{corr-table}. We were able to validate the dictionaries we received from MTurk in the 27 languages for which we had external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz. Across all 27 languages, 23\% of the source words from the Mechanical Turk dictionaries appeared in the external dictionaries, and could be validated. This was an average of 22\% per language.

\begin{table}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
&$\rho$\\
Language quality&0.41\\
Turker quality (languages pooled)&0.43\\
Avg. Turker quality (languages separate)&0.26\\
\hline\hline
\end{tabular}
\caption{Pearson correlation of quality measured by accuracy on control translations vs. quality measured by overlap with external dictionaries. Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers). Avg. Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations. The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
\label{corr-table}
\end{table}

\paragraph{Use of machine translation}
Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.  This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script. We measured the percent of translations received that exactly matched the translation returned from google translate. Results are show in figure \ref{google-match-bar}. Assignments averaged around 43\% overlap with google translate. Higher overlap with google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google. Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\footnotesize
\begin{figure*}
\begin{tabular}{lllll}
\multicolumn{4}{c}{Number of turkers per language}\\
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.74} (4)&0.73 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\normalsize
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{figure*}
\begin{tabular}{lllll}
\multicolumn{4}{c}{Number of turkers per language}\\
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.74} (4)&0.73 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\normalsize
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
